---
title: "OCD Comorbidity Meta-analysis: Across the Lifespan"
author: "Sharma E et al"
date: "26/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r packages, include=FALSE}
library(dplyr)
library(kableExtra)
library(metafor)
library(meta)
library(weightr)
```


```{r input, include=FALSE}

round2 <- function(x) {round(x, digits=1)} #Make a small function to round off digits to 1 (As these are only the descriptive tables)

df <- read.csv("Eesha OCD Comorb.csv")

df2 <- df %>% filter(Recruitment_Type != "Community") %>% select(StudyID, Country, Design, Total_N, 
                                                                 Age_Mean, Age_Group, AAO_Mean, 
                                                                 YBOCST_Mean, Instrument, Gender_Male_Perc, 29:218) %>% mutate_if(is.numeric, round2)  # Select only the important columns, round off to 1 decimal for everything 

df2$Age_Group <- factor(df2$Age_Group, levels = c("Pediatric", "Adult"))

df.var <- read.csv("Var_Names.csv") # this is a file with better labels for each disorder
df.var$No <- 1:nrow(df.var)

df.var2 <- read.csv("Var_Included.csv") # File with only the disorders that we're analyzing this time
df.var2$No <- 1:nrow(df.var2)

v1 <- sapply(df.var$Var, as.character) # a character vector, useful for running for loops
v2 <- sapply(df.var2$Var, as.character)

```


```{r metafunction, echo=F}

# This is my masterpiece: A customized function for making tables, with descriptives and summaries!!

metafunc <- function(x) {writeLines(paste0("<h3>Suppl Table ", 
                                            df.var2[df.var2$Var == x, "No"],". ",
                                            df.var2[df.var2$Var == x, "Proper_Name"],"</h3>"))
                          temp <- df2  %>% select(StudyID, Country, Total_N, Age_Mean, AAO_Mean, Age_Group, Gender_Male_Perc, YBOCST_Mean, Instrument, x)
                          temp <- temp %>% filter(!is.na(get(x)))
                          writeLines(paste0("-----------------------------------------", "\n"))
                          writeLines(paste0("Total number of studies that reported ", df.var2[df.var2$Var == x, "Proper_Name"], " = ", nrow(temp), "\n"))
                          writeLines(paste0("Number of pediatric studies that reported ", df.var2[df.var2$Var == x, "Proper_Name"], " = ", nrow(temp[temp$Age_Group == "Pediatric",]), "\n"))
                          if(nrow(temp) != 0) {
                          writeLines(paste0("Total N of OCD cases in studies that reported ", df.var2[df.var2$Var == x, "Proper_Name"], " = ", sum(temp$Total_N), "\n"))
                          writeLines(paste0("Total cases of ", df.var2[df.var2$Var == x, "Proper_Name"], " = ", sum(select(temp, x), na.rm = T), "\n"))
                          writeLines(paste0("-----------------------------------------", "\n"))
                          temp$No <- 1:nrow(temp)
                          temp <- temp %>% select(No, StudyID, Country, Total_N, Age_Mean, AAO_Mean, Age_Group, Gender_Male_Perc, YBOCST_Mean, Instrument, x)
                          temp2 <- temp
                          temp2$Perc <- round(select(temp, x)*100/select(temp, Total_N), digits = 1)
                          colnames(temp2) <- c("No", "Study", "Country", "Total OCD Subjects", "Mean Age", "Mean AAO", "Age Group", "% Males", "Mean (C)YBOCS-T","Diagnostic Instrument", x, paste0(x, " %"))
                          print(temp2 %>% kable(align= 'c', padding=4) %>% kable_styling(full_width = T))
                          cat("\n\n")
                          } else {writeLines("No studies here, move on!")
                                  writeLines(paste0("-----------------------------------------", "\n"))
                                  cat("\n")}
                          writeLines(paste0("</h3> ------------------------------------------------------------------------- </h3>"))
                          cat("\n")
                          cat("\n")
                            }
```

``` {r dummy, include=FALSE}
# This is just a dummy piece of code to take care of some annoying error messages!
metafunc("Any_AxisI_Life")

```

# ------------------------------------------------------------------------------------------

## Supplementary tables describing studies included in the meta-analysis for each comorbidity

#### ------------------------------------------------------------------------------------

#### Abbreviations used:

OCD - Obsessive-Compulsive Disorder; 
\n
AAO - Age at Onset of OCD; 
\n
(C)YBOCS-T - (Childhood) Yale-Brown Obsessive-Compulsive Scale Total Score; 
\n
MINI - Mini International Neuropsychiatric Interview; 
\n
SCID - Structured Clinical Interview for DSM; 
\n
ADIS - Anxiety Disorders Interview Schedule; 
\n
SADS - Schedule for affective Disorders and Schizophrenia; 
\n
K-SADS - Kidddie-SADS; 
\n
DIS - Diagnostic Interview Schedule

#### ------------------------------------------------------------------------------------

``` {r supptables, results='asis', R.options = list(width = 100)}
# Making all the tables, the easiest possible way!


for (i in v2) {metafunc(i)}
```

# ------------------------------------------------------------------------------------------
